Elite individuals, insitutions, and economic growth accounting

### 2024-04-05 presentation/main.tex
xgboost charts

\begin{frame}
\frametitle{Data Sources}
\begin{itemize}
    \item World Bank: World Development Indicators
    \item International Math Olympiad
    \item ARWU University Rankings
    \item Economist Democracy Scores
\end{itemize}
\end{frame}

@@

\begin{frame}{Rationale for variables}
    Capturing the ability of a country/region/education system to produce and identify elite talent is difficult. There are many potential omitted variables which may bias results.
\end{frame}

@@

>>>>

\begin{frame}
\frametitle{Data Sources}
\begin{itemize}
    \item World Bank: World Development Indicators
    \item International Math Olympiad
    \item ARWU University Rankings
    \item PISA Math Scores
    \item Economist Democracy Scores
\end{itemize}
\end{frame}

@@

\begin{frame}{Summary Statistics}
    Hello
\end{frame}

\begin{frame}{Rationale for variables}
    \begin{block}{IMO Scores}
        Indicator for a country's (and region's) ability to develop/identify pinncale STEM talent at high school level.
    \end{block}

    \begin{block}{ARWU Rankings}
        Indicator for a country's (and region's) ability to produce exellence in research output.
    \end{block}

    \begin{block}{Percent in PISA 99th percentile}
        When controlling for average PISA math scores, this is a partial indicator for whether general excellence in academics is encouraged/necessary.
    \end{block}
\end{frame}

@@

\begin{frame}{Relationships}
    Insert scatter plots for each of 3 key variables.
\end{frame}
